Very Preliminary Draft

### 2021-06-30 article/draft.tex
just testing
just testing again!

%Using social media data to verify the platforms' regulation policies regarding misinformation"

@@

During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content.\footnote{For Facebook, Twitter and Youtube see respectively the following updates: } As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms. Such targeted policies show the willingness of MSMP to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general. {\color{red} Say what they say they do + partnerships with fact-checkers + algorithms + community, Make point about ``recycling" existing policies (e.g. to tackle terrorism) and apply it to misinformation+ idea about academic community needs to be able to study this phenomenon and assess the impact of the policies, what effects they have etc.}

>>>>

Using social media data to verify the platforms' regulation policies regarding ``misinformation''

@@

During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content.\footnote{For Facebook, Twitter and Youtube see respectively the following updates: } As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms. Such targeted policies show the willingness of MSMP to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general. {\color{pink} Say what they say they do + partnerships with fact-checkers + algorithms + community, Make point about ``recycling" existing policies (e.g. to tackle terrorism) and apply it to misinformation+ idea about academic community needs to be able to study this phenomenon and assess the impact of the policies, what effects they have etc.}
